Translation Manual for Salamucha's Formalization of the \emph{Ex Motu} Argument

### 2017-05-31 Formalizations/Isabelle/Salamucha/Notation/TranslationManual.tex
Fix typo and add tex source to translation manual
Refactor Tex Source

\documentclass[english,ngerman,paper=a4,]{scrartcl}%
\input{Praeambel}%
%
\usepackage%
%[hidelinks]%
{hyperref} %%%% HYPERREF SOLLTE BIS AUF AUSNAHMEN IMMER DAS LETZTE PAKET SEIN %%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}%
%
%
%
%
%
%
\renewcommand{\baselinestretch}{1.50}\normalsize%
%\tableofcontents\newpage%
%
%%%%%%%%%%%%%%%%%%%%%

\makeatletter
% Remove \@date and spacing following it from \@maketitle
\patchcmd{\@maketitle}% <cmd>
  {{\usekomafont{date}{\@date \par}}%
    \vskip \z@ \@plus 1em}% <search>
  {}% <replace>
  {}{}% <success><failure>
\makeatother
%
\title{Translation Manual for Salamuchas Formalization of the Ex Motu Argument}
\maketitle
\section{Logical Notation}
%%
%

\begin{tabular}{|c|c|c|c|}
\hline 
\textbf{Name of Operator} & \textbf{Samalamucha first variant} & \textbf{Second variant} & \textbf{\enquote{Standard notation}} \\ 
\hline 
Conjunction & $p . q$ & $p \wedge q$ & $p \wedge q$ \\ 
\hline 
Disjunction & $p \vee q$ & $p \vee q$  & $p \vee q$ \\ 
\hline 
Negation & $\sim p$ & $\sim p$ & $\neg p$ \\ 
\hline 
(Material) Implication & $p \supset q$ & $p \rightarrow q$ & $p \rightarrow q$ \\ 
\hline 
Biconditional & $p \equiv q$ & $p \equiv q$ & $p \leftrightarrow q$ \\ 
\hline 
Universal Quantifier & $[x]. \phi (x)$ & $\wedge x \phi (x)$ & $\forall x. \phi (x)$ \\ 
\hline 
Existential Quantifier & $[\exists x]. \phi (x)$& $\vee x \phi (x)$ & $\exists x. \phi (x)$ \\ 
\hline 
\end{tabular}

\section{Definitions of relations, predicates, etc.}
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Notation} & \textbf{Name/Description} & \textbf{Definition} \\ 
\hline 
$x R y$ & Relation (at first!) & the usual \\ 
\hline 
$C'R$& Set of all elements of a relation & $x \in C'R \Leftrightarrow \exists t. (t R x \vee x R t)$ \\ 
\hline 
$K(R)$ & Ordering relation & transitive, irreflexive, connected relation \\ 
\hline 
$f x$ & x is in motion &  - \\ 
\hline 
$x R y$ & x moves y&  - \\ 
\hline 
$M_{x}(a)$ or $a M x$ & a is the proper part of x [sic] & -  \\ 
\hline
$xA_{s}y$ & x is in aspect S \emph{in actu} to y [emph. orig.] & -  \\ 
\hline 
$C x$ & x is a body & -  \\ 
\hline 
 $t_{i}Fx$ $t_i$ & $t_i$ is the duration of movement of x [sic] & -  \\ 
\hline 
 $F(t_i)$ or $Ht_i$ & $t_i$ is the finite period of time [sic]& -  \\ 
\hline 
\end{tabular}
%
%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{jurabib}
\bibliography{/home/knork/Dokumente/Latex/Philosophie.bib}

\end{document}

>>>>

\documentclass[english,paper=a4,]{scrartcl}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{kpfonts}
\usepackage{microtype}
\usepackage{babel}
\usepackage{geometry}%Alternativ typearea (KOMA)
\geometry{lmargin=2cm,tmargin=2cm,rmargin=1.5cm,bmargin=2cm}
\usepackage{marvosym}
\usepackage{tabularx}% Tabellen bestimmter Breite
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{xspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.50}\normalsize%%

\makeatletter
% Remove \@date and spacing following it from \@maketitle
\patchcmd{\@maketitle}% <cmd>
  {{\usekomafont{date}{\@date \par}}%
    \vskip \z@ \@plus 1em}% <search>
  {}% <replace>
  {}{}% <success><failure>
\makeatother
%
\title{Translation Manual for Salamucha's Formalization of the \emph{Ex Motu} Argument}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\section{Logical Notation}
%%
%

\begin{tabular}{|c|c|c|c|}
\hline 
\textbf{Name of Operator} & \textbf{Samalamucha's first version} & \textbf{Second version} & \textbf{\enquote{Standard notation}} \\ 
\hline 
Conjunction & $p . q$ & $p \wedge q$ & $p \wedge q$ \\ 
\hline 
Disjunction & $p \vee q$ & $p \vee q$  & $p \vee q$ \\ 
\hline 
Negation & $\sim p$ & $\sim p$ & $\neg p$ \\ 
\hline 
(Material) Implication & $p \supset q$ & $p \rightarrow q$ & $p \rightarrow q$ \\ 
\hline 
Biconditional & $p \equiv q$ & $p \equiv q$ & $p \leftrightarrow q$ \\ 
\hline 
Universal Quantifier & $[x]. \phi (x)$ & $\wedge x \phi (x)$ & $\forall x. \phi (x)$ \\ 
\hline 
Existential Quantifier & $[\exists x]. \phi (x)$& $\vee x \phi (x)$ & $\exists x. \phi (x)$ \\ 
\hline 
\end{tabular}

\section{Definitions of relations, predicates, etc.}
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Notation} & \textbf{Name/Description} & \textbf{Definition} \\ 
\hline 
$x R y$ & Relation (at first!) & the usual \\ 
\hline 
$C'R$& Set of all elements of a relation & $x \in C'R \Leftrightarrow \exists t. (t R x \vee x R t)$ \\ 
\hline 
$K(R)$ & Ordering relation & transitive, irreflexive, connected relation \\ 
\hline 
$f x$ & x is in motion &  - \\ 
\hline 
$x R y$ & x moves y&  - \\ 
\hline 
$M_{x}(a)$ or $a M x$ & a is the proper part of x [sic] & -  \\ 
\hline
$xA_{s}y$ & x is in aspect S \emph{in actu} to y [emph. orig.] & -  \\ 
\hline 
$C x$ & x is a body & -  \\ 
\hline 
 $t_{i}Fx$  & $t_i$ is the duration of movement of x [sic] & -  \\ 
\hline 
 $F(t_i)$ or $Ht_i$ & $t_i$ is the finite period of time [sic]& -  \\ 
\hline 
\end{tabular}
%
%%%%%%%%%%%%%%%%%%%%%%
\end{document}
